Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-02-06 additional_files/additional_file_1.tex
Adjust the format of the manuscript + supplemental data to fit an article manuscript format

\chapter{Supplemental data}
\label{supdata}

@@

% Detailed methods for some aspects of the paper
\section{Detailed methods}
\label{annexe-sv-gwas-detailed-methods}

\subsection{Discovery of structural variation from Illumina data}
\label{sv-gwas-sv-discovery-illumina}

@@

\subsection{Discovery of structural variation from Oxford Nanopore sequencing data}
\label{sv-gwas-sv-discovery-ont}

@@

\subsection{Discovery of structural variation from high-quality assemblies}
\label{sv-gwas-sv-discovery-assembly}

@@

\subsection{Genotyping structural variation using Paragraph}
\label{sv-gwas-sv-genotyping-paragraph}

@@

\subsection{Genotyping structural variation using the vg toolkit}
\label{sv-gwas-sv-genotyping-vg}

@@

\subsection{Comparison of WGS and SoySNP50K genotypes}
\label{annexe-sv-gwas-soysnp50k}
When we first analyzed the results from the GWAS analysis on all 389 samples,
we found discrepancies between the haplotypes at some loci and the expected
phenotype that should correspond to that haplotype for simple traits such as
flower color and seed coat color. Upon further analysis, we found that a
mismatch between the sequencing data and the identity of the accession was the
most probable cause of these discrepancies. In order to filter out all samples
for which this could be the case, we compared the genotypes of SNPs obtained
from the SoySNP50K array \cite{song2013} to those obtained from the Illumina WGS
data of the 385 samples that had a match in the GRIN database. Briefly, we
retrieved SoySNP50K genotype calls from SoyBase \citep{grant2010} and extracted
all SNPs with a MAF $\geq$ 0.1 in our population. We translated the positions
of these SNPs from assembly version 2 to assembly version 4 of Williams by
finding exact matches of 41-bp sequences surrounding the SNP positions. The
32,852 SNPs for which unambiguous positions could be found on genome assembly
version 4 were genotyped from the mapped WGS reads using \texttt{bcftools
mpileup} and \texttt{bcftools call}. We then used \texttt{bcftools gtcheck} to
compute the concordance of genotype calls between WGS samples and their
expected match in the SoySNP50K genotype dataset.  We identified 24 samples
with < 90\% concordance between the two genotype datasets and removed them from
the dataset, in addition to another sample for which concordance was over 90\%
but poor raw sequencing data quality (\%GC content) suggested contamination.
Following these filtering steps, 363 samples remained for GWAS analyses. The
concordance between WGS data and SoySNP50K genotypes is included in
Additional file 2.

% Detailed results that are not meant to fit the main paper
\section{Detailed results}
\label{annexe-sv-gwas-detailed-results}

@@

\subsection{Flower color}
\label{sv-gwas-flower-color}

@@

\subsection{Pubescence color}
\label{sv-gwas-pubescence-color}

@@

\subsection{Seed coat color}
\label{sv-gwas-seed-coat-color}

@@

\subsection{Stem termination type}
\label{sv-gwas-stem-termination}

@@

\subsection{Hilum color}
\label{sv-gwas-hilum-color}

@@

\subsection{Pod color}
\label{sv-gwas-pod-color}

@@

\subsection{Pubescence form}
\label{sv-gwas-pubesence-form}

@@

\subsection{Pubescence density}
\label{sv-gwas-pubescence-density}

@@

\subsection{Seed coat luster}
\label{sv-gwas-seed-coat-luster}

@@

\subsection{Maturity group}
\label{sv-gwas-maturity-group}

@@

\subsection{Resistance to \emph{Phytophthora sojae}}
\label{sv-gwas-resistance}

@@

\subsection{Seed oil content}
\label{sv-gwas-seed-oil-content}

@@

\subsection{Seed protein content}
\label{sv-gwas-seed-protein-content}

@@

% Supplemental tables
\section{Supplemental tables}
\label{annexe-sv-gwas-tables}

@@

% Supplemental figures
\section{Supplemental figures}
\label{annexe-sv-gwas-figures}

>>>>

\chapter*{Supplemental data}
\label{supdata}

% Format figure and table numbers to follow S1, S2, ...
\renewcommand\thefigure{S\arabic{figure}} 
\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand\thetable{S\arabic{table}}

@@

% Detailed methods for some aspects of the paper
\section*{Detailed methods}
\label{annexe-sv-gwas-detailed-methods}

\subsection*{Discovery of structural variation from Illumina data}
\label{sv-gwas-sv-discovery-illumina}

@@

\subsection*{Discovery of structural variation from Oxford Nanopore sequencing data}
\label{sv-gwas-sv-discovery-ont}

@@

\subsection*{Discovery of structural variation from high-quality assemblies}
\label{sv-gwas-sv-discovery-assembly}

@@

\subsection*{Genotyping structural variation using Paragraph}
\label{sv-gwas-sv-genotyping-paragraph}

@@

\subsection*{Genotyping structural variation using the vg toolkit}
\label{sv-gwas-sv-genotyping-vg}

@@

\subsection*{Comparison of WGS and SoySNP50K genotypes}
\label{annexe-sv-gwas-soysnp50k}
When we first analyzed the results from the GWAS analysis on all 389 samples,
we found discrepancies between the haplotypes at some loci and the expected
phenotype that should correspond to that haplotype for simple traits such as
flower color and seed coat color. Upon further analysis, we found that a
mismatch between the sequencing data and the identity of the accession was the
most probable cause of these discrepancies. In order to filter out all samples
for which this could be the case, we compared the genotypes of SNPs obtained
from the SoySNP50K array \cite{song2013} to those obtained from the Illumina WGS
data of the 385 samples that had a match in the GRIN database. Briefly, we
retrieved SoySNP50K genotype calls from SoyBase \citep{grant2010} and extracted
all SNPs with a MAF $\geq$ 0.1 in our population. We translated the positions
of these SNPs from assembly version 2 to assembly version 4 of Williams by
finding exact matches of 41-bp sequences surrounding the SNP positions. The
32,852 SNPs for which unambiguous positions could be found on genome assembly
version 4 were genotyped from the mapped WGS reads using \texttt{bcftools
mpileup} and \texttt{bcftools call}. We then used \texttt{bcftools gtcheck} to
compute the concordance of genotype calls between WGS samples and their
expected match in the SoySNP50K genotype dataset.  We identified 24 samples
with < 90\% concordance between the two genotype datasets and removed them from
the dataset, in addition to another sample for which concordance was over 90\%
but poor raw sequencing data quality (\%GC content) suggested contamination.
Following these filtering steps, 363 samples remained for GWAS analyses. The
concordance between WGS data and SoySNP50K genotypes is included in
Additional file 2.

% Detailed results that are not meant to fit the main paper
\section*{Detailed results}
\label{annexe-sv-gwas-detailed-results}

@@

\subsection*{Flower color}
\label{sv-gwas-flower-color}

@@

\subsection*{Pubescence color}
\label{sv-gwas-pubescence-color}

@@

\subsection*{Seed coat color}
\label{sv-gwas-seed-coat-color}

@@

\subsection*{Stem termination type}
\label{sv-gwas-stem-termination}

@@

\subsection*{Hilum color}
\label{sv-gwas-hilum-color}

@@

\subsection*{Pod color}
\label{sv-gwas-pod-color}

@@

\subsection*{Pubescence form}
\label{sv-gwas-pubesence-form}

@@

\subsection*{Pubescence density}
\label{sv-gwas-pubescence-density}

@@

\subsection*{Seed coat luster}
\label{sv-gwas-seed-coat-luster}

@@

\subsection*{Maturity group}
\label{sv-gwas-maturity-group}

@@

\subsection*{Resistance to \emph{Phytophthora sojae}}
\label{sv-gwas-resistance}

@@

\subsection*{Seed oil content}
\label{sv-gwas-seed-oil-content}

@@

\subsection*{Seed protein content}
\label{sv-gwas-seed-protein-content}

@@

% Supplemental tables
\section*{Supplemental tables}
\label{annexe-sv-gwas-tables}

@@

% Supplemental figures
\section*{Supplemental figures}
\label{annexe-sv-gwas-figures}

### 2023-02-06 additional_files/main_text.tex
Adjust the format of the manuscript + supplemental data to fit an article manuscript format

\chapter{\textit{k}-mer-based GWAS enhances the discovery of causal variants and candidate genes in soybean}
\label{kmer-gwas}

@@

\section{Abstract}

@@

\section{Introduction}
\label{sv-gwas-introduction}

@@

\section{Methods}
\label{sv-gwas-methods}

\subsection{Sample selection and processing of sequencing data}
\label{sv-gwas-sequencing-data}

@@

\subsection{Discovery and genotyping of SVs}
\label{sv-gwas-sv-discovery-genotyping}

@@

We merged the SVs called using each of these approaches using SVmerge
\citep{wong2010} and used the resulting set of candidate SVs for genotyping. We
used two programs with different genotyping models for genotyping this set of
SVs, Paragraph \citep{chen2019} and vg \citep{hickey2020}. In brief, Paragraph
genotypes each SV individually whereas vg builds a variation graph from a set
of candidate variants and then uses this graph to align sequence reads and
genotype variants.  Detailed methods regarding the SV discovery and genotyping
steps can be found in section \ref{annexe-sv-gwas-detailed-methods} of Appendix
\ref{annexe-sv-gwas}.

\subsection{Discovery and genotyping of SNPs and indels}
\label{sv-gwas-snp-discovery}

@@

The $\sim$7M SNPs and indels kept until this point were included in
the variation graph used for SV genotyping with the vg toolkit (see section
\ref{sv-gwas-sv-genotyping-vg} in Appendix \ref{annexe-sv-gwas}).

@@

\subsection{Computing the presence/absence table of \emph{k}-mers}
\label{sv-gwas-kmer-pav}

@@

\subsection{Phenotypic data}
\label{sv-gwas-phenotypic-data}

@@

Because of clear discrepancies between the observed haplotypes and the
reported phenotypes for some simple traits such as flower color and seed coat
color, we suspected possible errors in the identification of some of the
accessions. We compared the SNP genotypes derived from the SoySNP50K array
and our WGS data (see section \ref{annexe-sv-gwas-soysnp50k} in Appendix
\ref{annexe-sv-gwas} for detailed methods) at over 32,000 SNPs, and
identified 24 samples with < 90\% concordance between the two genotype
datasets. We removed them from the dataset in addition to another
sample that exhibited an atypical GC content suggesting contamination.
Following these filtering steps, 363 samples remained for GWAS analyses. The
concordance between WGS data and SoySNP50K genotypes is included in
Additional file 2 and averaged 98.3\% among retained lines while the
phenotypic data used in this study can be found in Additional file 3.

\subsection{GWAS analyses}
\label{sv-gwas-gwas-methods}

@@

\subsection{Analysis of significant \emph{k}-mers}
\label{sv-gwas-kmers-analysis-methods}

@@

\subsection{Downstream analyses of significant association signals}
\label{sv-gwas-methods-downstream}

@@

Because \cite{bandillo2015} and \cite{bandillo2017} used assembly version 1 of
Williams82, we converted the genomic positions of their signals from assembly
version 1 to version 4 by using the same method that was used for converting
SoySNP50K positions (see section \ref{annexe-sv-gwas-soysnp50k}).  The
boundaries of the signals thus translated to genome assembly version 4 were
used for comparison with the signals found in our analyses. For the analysis of
qualitative traits, we only compared our results to signals at named classical
loci and ignored previously reported minor signals with \emph{p}-values that
just barely made it above the significance threshold.

\subsection{Linking significant \emph{k}-mers to variants}
\label{sv-gwas-methods-linking-kmers}

@@

\subsection{Computation of LD between \emph{k}-mers}
\label{sv-gwas-ld-kmers}

@@

\subsection{Software used}
\label{sv-gwas-software-used}

@@

\section{Results and discussion}
\label{sv-gwas-results-discussion}

We analyzed a total of 13 traits using four different GWAS approaches, one
based on SNP and indel genotypes (Platypus), two based on SV genotypes (Paragraph and
vg), and another based on the presence/absence of \textit{k}-mers.
Because two or three different GWAS analyses were conducted on some traits, a
total of 22 GWAS analyses were performed using each of the four approaches.
Given the large volume of data that this represents, we will focus here on the
most noteworthy results. Readers interested in seeing detailed results on a
per-trait basis are referred to section \ref{annexe-sv-gwas-detailed-results}
in Appendix \ref{annexe-sv-gwas}. In particular, table \ref{signals_table}
provides a summary of the \textit{p}-values obtained by each approach at each
of the loci considered in this study.

\subsection{Loci with known genes or causal mutations}
\label{sv-gwas-results-cloned-genes}

@@

			\begin{tablenotes}
			\item[a] Platypus genotypes SNPs and indels
			\item[b] vg and Paragraph genotype SVs
			\item[c] Locus not discussed in main text. See section \ref{annexe-sv-gwas-detailed-results} in Appendix \ref{annexe-sv-gwas} for detailed results.
			\item[]- The approach detected no signal overlapping the gene.
			\item[]* The signal found at this locus overlaps the gene.
			\item[]** The region defined by the top 5\% (vg and Paragraph) or 1\% (Platypus and \textit{k}-mers) variants or \textit{k}-mers overlaps the gene.
			\item[]*** The most significantly associated marker or \textit{k}-mer is the causal variant.
			\end{tablenotes}

@@

\subsubsection{Flower color -- \textit{W1} locus}
\label{sv-gwas-main-results-flower-color-l1}

@@

We should note that when we first analyzed the results of the GWAS on flower
color, we observed that two accessions bearing the haplotype typically
associated with purple flowers were noted as having white flowers. Upon further
analysis, we found that the most likely cause of this discrepancy was a
mismatch between the genotype data and the identity of the accession for which
the phenotypic data was obtained. Indeed, when we compared SNP calls made
directly from the WGS data to those made using the SoySNP50K array, we observed
that these two samples had concordance rates of only 62\% and 70\%. To
prevent such mismatches from affecting our GWAS analyses, we computed the
concordance between genotype calls made from WGS data and the SoySNP50K array
for the whole population (see section \ref{sv-gwas-phenotypic-data} in the Methods) and
excluded 24 samples for which the concordance rate was below 90\%.

@@

\subsubsection{Pubescence color -- \textit{T} locus}
\label{sv-gwas-main-results-pubescence-color-t}

@@

\subsubsection{Pubescence color -- \textit{Td} locus}
\label{sv-gwas-main-results-pubescence-color-td}

@@

\subsubsection{Seed coat color - \textit{I} locus}
\label{sv-gwas-main-results-seed-coat-color-i}

@@

\subsubsection{Seed coat color - \textit{G} locus}
\label{sv-gwas-main-results-seed-coat-color-g}

@@

% Stem termination - Dt1 locus
\subsubsection{Stem termination type - \textit{Dt1} locus}
\label{sv-gwas-main-results-stem-termination-dt1}

@@

% Hilum color - T locus
\subsubsection{Hilum color -- \textit{T} locus}
\label{sv-gwas-main-results-hilum-color-t}

@@

% Hilum color - I locus
\subsubsection{Hilum color -- \textit{I} locus}
\label{sv-gwas-main-results-hilum-color-i}

@@

% Hilum color - R locus
\subsubsection{Hilum color -- \textit{R} locus}
\label{sv-gwas-main-results-hilum-color-r}

@@

% Pubescence density - Ps locus
\subsubsection{Pubescence density -- Ps locus}
\label{sv-gwas-main-results-pubescence-density-ps}

@@

% Seed coat luster - B locus
\subsubsection{Seed coat luster -- B locus}
\label{sv-gwas-main-results-seed-coat-luster-b}

@@

% Maturity group loci
\subsubsection{Maturity}
\label{sv-gwas-main-results-maturity}

@@

% Seed oil and protein
\subsubsection{Seed oil and protein content}
\label{sv-gwas-main-results-oil-protein}

@@

\subsection{Analysis of loci with unknown causal genes}
\label{sv-gwas-results}

% Pod color - L1 and L2 loci
\subsubsection{Pod color -- \textit{L1} and \textit{L2} loci}
\label{sv-gwas-main-results-pod-color-l1-l2}

@@

% Pubescence form - Pa1 and Pa2 loci
\subsubsection{Pubescence form -- \textit{Pa1} and \textit{Pa2} loci}
\label{sv-gwas-main-results-pubescence-form-pa1-pa2}

@@

% Resistance to Phytophthora sojae
\subsubsection{Resistance to \textit{P. sojae}}
\label{sv-gwas-main-results-psojae}

@@

% Stem terminination and pod color - novel loci
\subsubsection{Novel loci for stem termination and pod color}
\label{sv-gwas-main-results-novel-loci}

@@

\subsection{Potential of \emph{k}-mer-based GWAS}
\label{sv-gwas-potential-kmers}

@@

\subsection{Limitations and challenges of \emph{k}-mer-based GWAS}
\label{limitations-of-kmers-GWAS}

@@

\subsection{Use of SV genotypes for GWAS}
\label{use-of-svs-for-gwas}

@@

\section{Conclusion}

>>>>

\chapter*{\textit{k}-mer-based GWAS enhances the discovery of causal variants and candidate genes in soybean}
\label{kmer-gwas}

@@

\section*{Abstract}

@@

\section*{Introduction}
\label{sv-gwas-introduction}

@@

\section*{Methods}
\label{sv-gwas-methods}

\subsection*{Sample selection and processing of sequencing data}
\label{sv-gwas-sequencing-data}

@@

\subsection*{Discovery and genotyping of SVs}
\label{sv-gwas-sv-discovery-genotyping}

@@

We merged the SVs called using each of these approaches using SVmerge
\citep{wong2010} and used the resulting set of candidate SVs for genotyping. We
used two programs with different genotyping models for genotyping this set of
SVs, Paragraph \citep{chen2019} and vg \citep{hickey2020}. In brief, Paragraph
genotypes each SV individually whereas vg builds a variation graph from a set
of candidate variants and then uses this graph to align sequence reads and
genotype variants.  Detailed methods regarding the SV discovery and genotyping
steps can be found in Supplemental data.

\subsection*{Discovery and genotyping of SNPs and indels}
\label{sv-gwas-snp-discovery}

@@

The $\sim$7M SNPs and indels kept until this point were included in
the variation graph used for SV genotyping with the vg toolkit (see
Supplemental data).

@@

\subsection*{Computing the presence/absence table of \emph{k}-mers}
\label{sv-gwas-kmer-pav}

@@

\subsection*{Phenotypic data}
\label{sv-gwas-phenotypic-data}

@@

Because of clear discrepancies between the observed haplotypes and the
reported phenotypes for some simple traits such as flower color and seed coat
color, we suspected possible errors in the identification of some of the
accessions. We compared the SNP genotypes derived from the SoySNP50K array
and our WGS data (see Supplemental data
for detailed methods) at over 32,000 SNPs, and
identified 24 samples with < 90\% concordance between the two genotype
datasets. We removed them from the dataset in addition to another
sample that exhibited an atypical GC content suggesting contamination.
Following these filtering steps, 363 samples remained for GWAS analyses. The
concordance between WGS data and SoySNP50K genotypes is included in
Additional file 2 and averaged 98.3\% among retained lines while the
phenotypic data used in this study can be found in Additional file 3.

\subsection*{GWAS analyses}
\label{sv-gwas-gwas-methods}

@@

\subsection*{Analysis of significant \emph{k}-mers}
\label{sv-gwas-kmers-analysis-methods}

@@

\subsection*{Downstream analyses of significant association signals}
\label{sv-gwas-methods-downstream}

@@

Because \cite{bandillo2015} and \cite{bandillo2017} used assembly version 1 of
Williams82, we converted the genomic positions of their signals from assembly
version 1 to version 4 by using the same method that was used for converting
SoySNP50K positions (see Supplemental data).  The
boundaries of the signals thus translated to genome assembly version 4 were
used for comparison with the signals found in our analyses. For the analysis of
qualitative traits, we only compared our results to signals at named classical
loci and ignored previously reported minor signals with \emph{p}-values that
just barely made it above the significance threshold.

\subsection*{Linking significant \emph{k}-mers to variants}
\label{sv-gwas-methods-linking-kmers}

@@

\subsection*{Computation of LD between \emph{k}-mers}
\label{sv-gwas-ld-kmers}

@@

\subsection*{Software used}
\label{sv-gwas-software-used}

@@

\section*{Results and discussion}
\label{sv-gwas-results-discussion}

We analyzed a total of 13 traits using four different GWAS approaches, one
based on SNP and indel genotypes (Platypus), two based on SV genotypes (Paragraph and
vg), and another based on the presence/absence of \textit{k}-mers.
Because two or three different GWAS analyses were conducted on some traits, a
total of 22 GWAS analyses were performed using each of the four approaches.
Given the large volume of data that this represents, we will focus here on the
most noteworthy results. Readers interested in seeing detailed results on a
per-trait basis are referred to
Supplemental data. In particular, table \ref{signals_table}
provides a summary of the \textit{p}-values obtained by each approach at each
of the loci considered in this study.

\subsection*{Loci with known genes or causal mutations}
\label{sv-gwas-results-cloned-genes}

@@

			\begin{tablenotes}
			\item[a] Platypus genotypes SNPs and indels
			\item[b] vg and Paragraph genotype SVs
			\item[c] Locus not discussed in main text. See Supplemental data for detailed results.
			\item[]- The approach detected no signal overlapping the gene.
			\item[]* The signal found at this locus overlaps the gene.
			\item[]** The region defined by the top 5\% (vg and Paragraph) or 1\% (Platypus and \textit{k}-mers) variants or \textit{k}-mers overlaps the gene.
			\item[]*** The most significantly associated marker or \textit{k}-mer is the causal variant.
			\end{tablenotes}

@@

\subsubsection*{Flower color -- \textit{W1} locus}
\label{sv-gwas-main-results-flower-color-l1}

@@

We should note that when we first analyzed the results of the GWAS on flower
color, we observed that two accessions bearing the haplotype typically
associated with purple flowers were noted as having white flowers. Upon further
analysis, we found that the most likely cause of this discrepancy was a
mismatch between the genotype data and the identity of the accession for which
the phenotypic data was obtained. Indeed, when we compared SNP calls made
directly from the WGS data to those made using the SoySNP50K array, we observed
that these two samples had concordance rates of only 62\% and 70\%. To
prevent such mismatches from affecting our GWAS analyses, we computed the
concordance between genotype calls made from WGS data and the SoySNP50K array
for the whole population (see the Methods section) and
excluded 24 samples for which the concordance rate was below 90\%.

@@

\subsubsection*{Pubescence color -- \textit{T} locus}
\label{sv-gwas-main-results-pubescence-color-t}

@@

\subsubsection*{Pubescence color -- \textit{Td} locus}
\label{sv-gwas-main-results-pubescence-color-td}

@@

\subsubsection*{Seed coat color - \textit{I} locus}
\label{sv-gwas-main-results-seed-coat-color-i}

@@

\subsubsection*{Seed coat color - \textit{G} locus}
\label{sv-gwas-main-results-seed-coat-color-g}

@@

% Stem termination - Dt1 locus
\subsubsection*{Stem termination type - \textit{Dt1} locus}
\label{sv-gwas-main-results-stem-termination-dt1}

@@

% Hilum color - T locus
\subsubsection*{Hilum color -- \textit{T} locus}
\label{sv-gwas-main-results-hilum-color-t}

@@

% Hilum color - I locus
\subsubsection*{Hilum color -- \textit{I} locus}
\label{sv-gwas-main-results-hilum-color-i}

@@

% Hilum color - R locus
\subsubsection*{Hilum color -- \textit{R} locus}
\label{sv-gwas-main-results-hilum-color-r}

@@

% Pubescence density - Ps locus
\subsubsection*{Pubescence density -- Ps locus}
\label{sv-gwas-main-results-pubescence-density-ps}

@@

% Seed coat luster - B locus
\subsubsection*{Seed coat luster -- B locus}
\label{sv-gwas-main-results-seed-coat-luster-b}

@@

% Maturity group loci
\subsubsection*{Maturity}
\label{sv-gwas-main-results-maturity}

@@

% Seed oil and protein
\subsubsection*{Seed oil and protein content}
\label{sv-gwas-main-results-oil-protein}

@@

\subsection*{Analysis of loci with unknown causal genes}
\label{sv-gwas-results}

% Pod color - L1 and L2 loci
\subsubsection*{Pod color -- \textit{L1} and \textit{L2} loci}
\label{sv-gwas-main-results-pod-color-l1-l2}

@@

% Pubescence form - Pa1 and Pa2 loci
\subsubsection*{Pubescence form -- \textit{Pa1} and \textit{Pa2} loci}
\label{sv-gwas-main-results-pubescence-form-pa1-pa2}

@@

% Resistance to Phytophthora sojae
\subsubsection*{Resistance to \textit{P. sojae}}
\label{sv-gwas-main-results-psojae}

@@

% Stem terminination and pod color - novel loci
\subsubsection*{Novel loci for stem termination and pod color}
\label{sv-gwas-main-results-novel-loci}

@@

\subsection*{Potential of \emph{k}-mer-based GWAS}
\label{sv-gwas-potential-kmers}

@@

\subsection*{Limitations and challenges of \emph{k}-mer-based GWAS}
\label{limitations-of-kmers-GWAS}

@@

\subsection*{Use of SV genotypes for GWAS}
\label{use-of-svs-for-gwas}

@@

\section*{Conclusion}

### 2023-02-06 additional_files/manuscript.tex
Adjust the format of the manuscript + supplemental data to fit an article manuscript format

\usepackage[utf8]{inputenc} % declare encoding as utf8
\usepackage{graphicx} % to enable \includegraphics
\usepackage{flafter} % to make sure floats appear after their position in text
\usepackage{pdflscape} % allow some pages to be in landscape orientation
\usepackage{layout} % for debugging purposes, looking at page layout
\usepackage[margin=1in]{geometry} % leaves more space for text body
\usepackage[hidelinks]{hyperref} % hyperlinks from list of figures/tables
\usepackage[labelfont=bf]{caption} % format captions and make links go to figure instead of caption
\usepackage{csvsimple} % read and display csv files as tables
\usepackage{booktabs} % prettier tables
\usepackage{threeparttable} % easy addition of footnotes below tables
\usepackage{textcomp} % makes the \textdegree command available
\usepackage{tocloft} % formatting the lists of tables and figures
\usepackage{xcolor} % enable text coloring
\usepackage{calc} % makes \widthof available to set the width of the last column
\usepackage{array} % using command \arraybackslash to restore the definition of \\ after \centering
\usepackage{longtable} % allow tables to span more than one page
\usepackage{threeparttablex} % threeparttable for longtable
\usepackage{capt-of} % put caption on next page
\usepackage{ccaption}
\usepackage{listings}
\usepackage{datatool} % allows fetching key-value pairs from a text file
\usepackage[sectionbib]{natbib}
\usepackage{chapterbib}

@@

@@

% Formatting the table of contents/subsection
\renewcommand{\contentsname}{Supplemental methods}

% Formatting the list of tables
\renewcommand{\listtablename}{Supplemental tables} % Write "Supplemental tables" instead of "List of tables"
\renewcommand\cfttabpresnum{Table } % Write "Table" before table number in list of tables
\setlength{\cfttabnumwidth}{6em} % Spacing before captions
\setlength{\cftbeforefigskip}{1ex} % Vertical spacing between entries

% Formatting the list of figures
\renewcommand{\listfigurename}{Supplemental figures} % Write "Supplemental figures" instead of "List of figures"
\renewcommand\cftfigpresnum{Figure } % Write "Figure" before fig number in list of figures
\setlength{\cftfignumwidth}{6em} % Spacing before captions
\setlength{\cftbeforetabskip}{1ex} % Vertical spacing between entries

@@

% Format figure and table numbers to follow S1, S2, ...
\renewcommand\thefigure{S\arabic{figure}} 
\renewcommand\thetable{S\arabic{table}}

>>>>

\usepackage[utf8]{inputenc} % declare encoding as utf8
\usepackage[T1]{fontenc} % declare encoding as utf8
\usepackage{graphicx} % to enable \includegraphics
\usepackage{flafter} % to make sure floats appear after their position in text
\usepackage{pdflscape} % allow some pages to be in landscape orientation
\usepackage{layout} % for debugging purposes, looking at page layout
\usepackage[margin=1in]{geometry} % leaves more space for text body
\usepackage[hidelinks]{hyperref} % hyperlinks from list of figures/tables
\usepackage[labelfont=bf]{caption} % format captions and make links go to figure instead of caption
\usepackage{csvsimple} % read and display csv files as tables
\usepackage{booktabs} % prettier tables
\usepackage{threeparttable} % easy addition of footnotes below tables
\usepackage{textcomp} % makes the \textdegree command available
\usepackage{tocloft} % formatting the lists of tables and figures
\usepackage{xcolor} % enable text coloring
\usepackage{calc} % makes \widthof available to set the width of the last column
\usepackage{array} % using command \arraybackslash to restore the definition of \\ after \centering
\usepackage{longtable} % allow tables to span more than one page
\usepackage{threeparttablex} % threeparttable for longtable
\usepackage{capt-of} % put caption on next page
\usepackage{ccaption}
\usepackage{listings}
\usepackage{datatool} % allows fetching key-value pairs from a text file
\usepackage[sectionbib]{natbib}
\usepackage{chapterbib}
\usepackage{setspace}

@@

% Adjust line spacing to 1.5
\onehalfspacing

@@

@@
